---
title: "hw_02"
output: 
  html_document:
    keep_md: true
editor_options: 
  chunk_output_type: inline
---

## Overview

The goal is to explore a dataset. In particular, to begin to establish a workflow for data frames or “tibbles”. This homework will use dplyr and ggplot2 to do some description and visualization.

## library the data set
```{r}
library(gapminder)
library(tidyverse)
```

## Explore the gapminder object:
1. Is it a data.frame, a matrix, a vector, a list?
```{r}
class(gapminder)
```
Answer: The object of gapminder is a "data.frame". 

2. What is its class?
```{r}
class(gapminder)
```
Answer: The class of gapminder is a "tbl_df". 

3,4. How many variables/columns and rows/observations?
```{r}
ncol(gapminder)
nrow(gapminder)
```
Answer: There are 6 colums and 1704 rows. 

5. Can you get these facts about “extent” or “size” in more than one way? Can you imagine different functions being useful in different contexts?
```{r}
str(gapminder)
glimpse(gapminder)
summary(gapminder)
ls(gapminder)
```
Answer: "str"" function can get these facts, such as classes, objects, variables.  Similarly, "glimpse"" can return the details of dataset while this method tries to show you as much data as possible. Another userful function is "summary"", which returns the values such as median, mean, max of the each variable. Function "ls"" is also useful in returning the variables.

6. What data type is each variable?
Answer: according to results of questions 5, the data of each variable is shown as below:
$ country   <fct> 
$ continent <fct> 
$ year      <int> 
$ lifeExp   <dbl> 
$ pop       <int> 
$ gdpPercap <dbl>

## Explore individual variables
1. What are possible values (or range, whichever is appropriate) of each variable?
```{r}
## let's make a data frame containing the columns year, pop, continent from the gapminder dat.
select(gapminder,year,pop, continent) %>% 
  arrange(year, pop) %>% # Then order by year, then by pop
  filter(pop > 1000000000 & year >= 2002) %>% # Then fliter the data with population more than 1 billion and year more than 2002
  knitr::kable()
```

2. What values are typical? What’s the spread? What’s the distribution? Etc., tailored to the variable at hand.
```{r}
##scale can be viewed use bar chart
  ggplot(gapminder,aes(x = continent)) + 
  geom_bar() 
```
```{r}
gapminder %>%
##distribution can be viewd use summary
  select(year, pop,continent, lifeExp) %>%
  summary() %>% 
  knitr::kable()
```
```{r}
##The counts for variables for each year are the same (142). This happens in country (12) as well
table(gapminder$year) %>% 
  knitr::kable()
table(gapminder$country) %>% 
  knitr::kable()
```

## Explore various plot types
Make a few plots, probably of the same variable you chose to characterize numerically. 
Let's see the relationship between life expectancy and continent
```{r}
PLOT <- ggplot(gapminder, aes(x=continent, y=lifeExp))
```

1. scatterplot
```{r}
  PLOT + geom_point() +
  ggtitle("Scatter plot of Life Expectancy")
```
2. box plot
```{r}
 PLOT + geom_boxplot() +
    ggtitle("Scatter plot of Life Expectancy")
```
3. violin plot
```{r}
 PLOT + geom_violin() +
    ggtitle("Scatter plot of Life Expectancy")
```
4. overlap geom_violin and jitter plot
```{r}
 PLOT + geom_violin() +
  geom_jitter(alpha = 0.1)
```
5. let's see the life expantancy in Americas with popolation more than 50 milion
```{r}
 gapminder %>% 
  filter(continent == "Americas") %>% 
  filter(pop >= 50000000) %>% 
  ggplot(aes(year, lifeExp, group = 1)) + 
  facet_grid(~country) +
  geom_violin() +
  geom_jitter(alpha = 0.1)
```

6. let's compare lifeExp in Americas and in Asia with popolation more than 50 milion
```{r}
 gapminder %>% 
  filter(continent == "Americas" | continent == "Asia") %>% 
  filter(pop >= 50000000) %>% 
  ggplot(aes(year, lifeExp, group = 1)) + 
  facet_grid(~continent) +
  geom_violin() +
  geom_jitter(alpha = 0.1)
```

## But I want to do more!
```{r}
filter(gapminder, country == c("Rwanda", "Afghanistan")) %>% 
knitr::kable()
```
Answer: the c("Rwanda", "Afghanistan") dose not return "Rwanda" | "Afghanistan". Therefore, the logical algiritem is not [country == "Rwanda" | country == "Afghanistan"].

One possible solution is given by:
```{r}
  filter(gapminder, country == "Rwanda" | country == "Afghanistan") %>%
  knitr::kable()
```

